SU($n$) spin models near the Heisenberg critical point

### 2020-03-22 collective_sun/sun_perturbation.tex
simplified explanation/counting of different index assignments

each dot in a region $S$ of a diagram $g$, of which tensor factor of
$w_\alpha$ and $X_\alpha$ (for all $\alpha\in S$) that dot is
associated with.  The only catch is that such choices treat all dots
in $g$ as distinct, whereas the $g_S$ dots within region $S$ of $g$
are actually indistinguishable.  The assignment
$X_1\p{a,b,c} X_2\p{a,b}$, for example, is the same as
$X_1\p{b,a,c} X_2\p{b,a}$.  We denote the set of all distinct index
assignments according to $g$ by $\L\p{g}$.  The number of such
assignments is

@@

  \abs{\L\p{g}}
  = \sp{\prod_{\alpha\in\ZZ_p} \C\p{ g_S : \alpha\in S }}
  \sp{\prod_{S\in\PP^*\p{\ZZ_p}} \p{g_S!}^{\abs{S}}}
  \sp{\prod_{S\in\PP^*\p{\ZZ_p}} g_S!}^{-1}
  = \m M! \sp{\prod_{S\in\PP^*\p{\ZZ_p}} g_S!}^{-1},
  \label{eq:index_assignment_num}

@@

where the first product in \eqref{eq:index_assignment_num} contains
multinomial coefficients
  \C\p{a_1,a_2,\cdots,a_m}
  \equiv \f{\p{a_1+a_2+\cdots+a_m}!}{a_1!a_2!\cdots a_m!}
that account for the number of ways to partition the $M_\alpha$
indices of each $w_\alpha$ and $X_\alpha$ into sets of shared indices
as specified by $g$, the second product in
\eqref{eq:index_assignment_num} accounts for the number of ways to
permute each set of shared indices on each $w_\alpha$ and $X_\alpha$,
and the third product in \eqref{eq:index_assignment_num} accounts for
the treatment of the dots within each region $S$ of $g$ as
distinguishable, when in fact they are not.  Altogether, we have

>>>>

each of the $M_\alpha$ tensor factors of $w_\alpha$ and $X_\alpha$, of
which dot in the diagram $g$ that tensor factor is associated with
(i.e.~out of the $M_\alpha$ dots within circle $\alpha$).  There are
nominally $M_\alpha!$ such choices for a given $\alpha$, and therefore
$\prod_{\alpha\in\ZZ_p}M_\alpha!=\m M!$ choices total.  The only catch
is that these choices treat all dots in $g$ as distinct, whereas the
$g_S$ dots within region $S$ of $g$ are actually indistinguishable.
The assignment $X_1\p{a,b,c} X_2\p{a,b}$, for example, is the same as
$X_1\p{b,a,c} X_2\p{b,a}$.  In general, the treatment of the $g_S$
indistinguishable dots within region $S\in\PP^*\p{\ZZ_p}$ of $g$ as
distinguishable results in over-counting distinct index assignments by
a factor of $g_S!$.  Denoting the set of all distinct index
assignments according to $g$ by $\L\p{g}$, the number of such
assignments is therefore

@@

  \abs{\L\p{g}} = \m M! \sp{\prod_{S\in\PP^*\p{\ZZ_p}} g_S!}^{-1}.

@@

Altogether, we have
